Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-11 paper/paper.tex
pass on NLP par

% For the classification of ``code'' vs. ``not code'', we used a
% pipeline of two Neural Networks (NN), a popular design for solving NLP
% classification problems~\cite{kusner2015word}. The first net in the
% pipeline takes as input an arbitrary sentence and produces on output a
% characterization vector for that sentence. The second net in the
% pipeline takes that vector on input and produces a yes/no answer,
% determining whether or not the input sentence was code.  During the
% training phase, the second neural net in the pipeline takes
% additionally on input the value for the class attribute for the sample;
% in this case, ``code'' or ``not code''. More in detail, for the first
% net, we used word2vec~\cite{mikolov2013distributed}, a popular NLP
% technique to produce word embeddings. A word embedding is a mapping of
% words to vectors of real numbers. For the second net, we used a
% multi-layer perceptron~\cite{Rumelhart:1986:LIR:104279.104293} to
% infer the probability of the input belonging or not to the class. The
% classifier labels the input input as code if the predicted probability
% of the input being code is 0.7 or higher. We used a corpus with 25K
% samples of English paragraphs and 25K snippets of \js{} code to train
% and test the classifier and obtained an accuracy of 98\%. This
% classifier is publicly available from our website as a separate
% component.
\Igor{
For the classification of ``code'' vs. ``not code'', we used popular 
techniques for solving NLP classification problems~\cite{kusner2015word}.
More in detail, we used word2vec~\cite{mikolov2013distributed},
a popular NLP technique to produce word embeddings. A word embedding is 
a mapping of words to vectors of real numbers. We chose word2vec for
two mainly reasons: i) similarity between sentences and ii)
to obtaining a low-dimensional vector that can be used in
a traditional classifier. The next step we used a
 multi-layer perceptron~\cite{Rumelhart:1986:LIR:104279.104293}
to infer the probability of the input belonging or not to the class based 
on the distance of similarity of sentences, the classifier takes that vector
on input and produces a ``code'' or ``not code'' answer. The classifier labels
the input as code if the predicted probability of the input being code is 0.7 or higher. 
We used a corpus with 25K samples of English paragraphs and 25K snippets of \js{} code to train
and test the classifier and obtained an accuracy of 98\%. This
classifier is publicly available from our website as a separate
component.
}

>>>>

% For the classification of ``code'' vs. ``not code'', we used a
% pipeline of two Neural Networks (NN), a popular design for solving NLP
% classification problems~\cite{kusner2015word}. The first net in the
% pipeline takes as input an arbitrary sentence and produces on output a
% characterization vector for that sentence. The second net in the
% pipeline takes that vector on input and produces a yes/no answer,
% determining whether or not the input sentence was code.  During the
% training phase, the second neural net in the pipeline takes
% additionally on input the value for the class attribute for the sample;
% in this case, ``code'' or ``not code''. More in detail, for the first
% net, we used word2vec~\cite{mikolov2013distributed}, a popular NLP
% technique to produce word embeddings. A word embedding is a mapping of
% words to vectors of real numbers. For the second net, we used a
% multi-layer perceptron~\cite{Rumelhart:1986:LIR:104279.104293} to
% infer the probability of the input belonging or not to the class. The
% classifier labels the input input as code if the predicted probability
% of the input being code is 0.7 or higher. We used a corpus with 25K
% samples of English paragraphs and 25K snippets of \js{} code to train
% and test the classifier and obtained an accuracy of 98\%. This
% classifier is publicly available from our website as a separate
% component.

For the classification of ``code'' vs. ``nocode'', we used popular
techniques for solving NLP classification
problems~\cite{kusner2015word}.  First, we used
word2vec~\cite{mikolov2013distributed}, a popular NLP technique to
produce word embeddings. A word embedding is a mapping of words to
vectors of real numbers. Then, we used a multi-layer
perceptron~\cite{Rumelhart:1986:LIR:104279.104293} to infer the
probability of the input belonging or not to the class based on the
distance between sentences (\ie{}, the distance from an input sentence
to a code example or to a nocode example) as induced by the distance
of comprising words computed with word2vec. The classifier labels the
input as code if the predicted probability of the input being code is
0.7 or higher.  We used a corpus with 25K samples of English
paragraphs and 25K snippets of \js{} code to train and test the
classifier and obtained an accuracy of 98\%. This classifier is
publicly available from our website as a separate component.

% We chose word2vec for two main reasons: i) similarity between
% sentences and ii) to obtaining a low-dimensional vector that can be used in a traditional classifier.
